### 2016-09-30 results.tex
no message

\begin{theorem}\label{thm3}\label{thm:bf-correctness}
Fix $k,m,n,r>0$, a set~$\elts$, and let $\setprim_{\mathrm{Bloom}}= (\Rep, \Qry)$ be classical Bloom filter (set-membership) data structure over~$\elts$. For any adversary~$A$ that makes a total of~$q_T$ queries to the $\Test$ oracle, and $q_R$ queries to the RO, and has time-complexity~$O(t)$,
\[
\AdvCorrect{\setprim_{\mathrm{Bloom}},r}{A} \leq  {\dbinom{q_T + q_H}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
\]
\end{theorem}
We note that Kirsch and Mitzenmacher~\cite{xxx} show
that the ($r=1$, zero-query) error-probability for~$\setprim_\mathrm{Bloom}$ is
always within $O(1/n)$ of $(1-e^{-kn/m})^k$, although the asymptotic
rate of convergence is faster than~$1/n$.  The multiplicative (``hybrid'') term arises as a result
of moving from the adaptive to the zero-query setting.
Finally, $\binom{q_T+q_H}{r} \leq (q_T+q_H)^r$ (with reasonable tightness when~$r$ is small) in
which case the final term in the bound behaves as
$((q_T+q_H) (1-e^{-kn/m})^k + O(q/n) )^r$; loosely, this is the bound one expects for
trying to find a single correctness error (in this case, a false positive) in each of~$r$ independent``rounds'', each round
consisting of~$(q_T+q_H)$ attempts.
\input{BF_correctness}

@@

\subsection{Domain-separated PRF-Hash}
%\heading{Construction of PRF with domain separation.}
\heading{Correctness. }
Let $\setprim_{\mathrm{ds}}= (\Rep, \Qry)$ be the set-membership data
structure defined on the right-side of Figure~\ref{fig:lin-and-ds}.
As with the preceding theorem, the following says (informally) that
if~$F$ is a secure PRF, then this domain-separated PRF construction is
correct against adaptive adversaries.
% \tsnote{Not really appropriate to say this next thing; I'll add a new section that addresses bigram DS-PRF hash.}
% We note that Neidermayer et
% al. in~\cite{xxx} suggest replacing the linear-PRF hash functions in
% the previous construction with independently keyed PRFs as a way to
% thwart their attacks.  The construction we consider now achieves the
% same end, albeit via explict domain separation rather than separate
% keys.

@@

\begin{theorem}[{\rm SS-privacy of bigram linear-PRF}]\label{thm:bi-lin-ss}
Let $\setprim_{\bilin}= (\Rep, \Qry)$ be the set-membership data structure described in Figure~\ref{fig:neidermayer}, but instantiated with $F_{K}$ replaced by a random functions~$\rho$.  Let $\leak_{\mathsf{abl}}$ be the leakage function just described.   Let~$\elts=\{\mathrm{a,b,c}\}^*$. Let $n=3$,  $m=3\alpha $ for integer $\alpha >> 1$, and let, $k = \lceil \ln(2) \alpha \rceil$.\tsnote{This value of~$k$ is from the classical analysis for minimizing the FP rate for a Bloom filter, and is set this way for compatibility with classical results.  It isn't used in any essential way in the proof sketch.}  Let~$A$ be the adversary in Figure~\ref{fig:adv-bi-lin-ss}.  Then for any simulator $\Sim$, the advantage $\AdvPrivSS{\setprim_{\bilin},\leak_{\mathsf{abl}}}{A,\Sim}$ can be made arbitrarily close to $1/2$ by choice of~$\alpha$.
\end{theorem}
\begin{proof}\tsnote{still a bit sketchy but believable}
On input the set~$S$ produced by~$A$, the $\Rep$ algorithm turns $x_1=$'cab', $x_2=$'bab' and $x_3$ into their respective bigram sets: $B_{x_1}=\{\sqcup\mathrm{c},\mathrm{ca},\mathrm{ab},\mathrm{b}\sqcup\}$, $B_{x_2}=\{\sqcup\mathrm{b},\mathrm{ba},\mathrm{ab}, \mathrm{b}\sqcup \}$; the set $B_{x_3}$ will be either $\{\sqcup\mathrm{c},\mathrm{ca},\mathrm{ab},\mathrm{ba}, \mathrm{a}\sqcup\}$, or $\{\sqcup\mathrm{c},\mathrm{ca},\mathrm{ab},\mathrm{bc}, \mathrm{c}\sqcup\}$, each with probability 1/2.  It then produces $\alpha$-bit arrays $M_1, M_2, M_3$ by hashing the corresponding bigram sets using the hash functions $h_j(s)=\rho_1(s)+ j\rho_2(s) \bmod m$.  Note that for sufficiently large~$m$, each of $M_1,M_2$ will contain exactly $4k$ positions set to 1; this is with overwhelming probability, up to collisions in the hash functions for different bigrams within a given bigram set.  Likewise, $M_{1,2}=M_1 \vee M_2$ will have exactly $6k$ positions set to 1, because $B_{x_1}$ and $B_{x_2}$ share $\mathrm{ab}$ and $\mathrm{a}\sqcup$.

@@

\begin{theorem}[{\rm Correctness of private-$M$ GBF in the ROM}]\fixme{FINISH! (Animesh?)}
Fix $k,m,n,r,\lambda>0$, and let $\setprim_{\mathrm{gbf}}=(\Rep, \Qry)$ be the private-$M$ garbled Bloom filter. For any adversary~$A$ that makes a total of~$q_T$ queries to the $\Test$ oracle, and $q_R$ queries to the RO, and has time-complexity~$O(t)$,
\[
\AdvCorrect{\setprim_{\mathrm{gbf}},r}{A} \leq  {\dbinom{q_T}{r}} \left( \dfrac{1}{2^{\lambda}} \right)^r\,.
\]
\end{theorem}

>>>>

\begin{theorem}\label{thm3}\label{thm:bf-correctness}
Fix $k,m,n,r>0$ and a set~$\elts$, and let
$\setprim_{\mathrm{Bloom}}= (\Rep, \Qry)$ be the classical Bloom
filter (set-membership) data structure over~$\elts$. For any
adversary~$A$ that makes a total of~$q_T$ queries to the $\Test$
oracle, and $q_R$ queries to the RO, and has time-complexity~$O(t)$,
\[
\AdvCorrect{\setprim_{\mathrm{Bloom}},r}{A} \leq  {\dbinom{q_T + q_H}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
\]
\end{theorem}
We note that Kirsch and Mitzenmacher~\cite{xxx} show
that the ($r=1$, zero-query) error-probability for~$\setprim_\mathrm{Bloom}$ is
always within $O(1/n)$ of $(1-e^{-kn/m})^k$, although the asymptotic
rate of convergence is faster than~$1/n$.  The multiplicative (``hybrid'') term arises as a result
of moving from the adaptive to the zero-query setting.
Finally, $\binom{q_T+q_H}{r} \leq (q_T+q_H)^r$ (with reasonable tightness when~$r$ is small) in
which case the final term in the bound behaves as
$((q_T+q_H) (1-e^{-kn/m})^k + O(q/n) )^r$; loosely, this is the bound one expects for
trying to find a single correctness error (in this case, a false positive) in each of~$r$ independent``rounds'', each round
consisting of~$(q_T+q_H)$ attempts.
\input{BF_correctness}

@@

\subsection{Domain-Separated PRF-Hash}
\jnote{Give English-language description of scheme before turning to
analysis of correctness.}

%\heading{Construction of PRF with domain separation.}
\heading{Correctness. } Let $\setprim_{\mathrm{ds}}= (\Rep, \Qry)$
be the set-membership data structure defined on the right-side of
Figure~\ref{fig:lin-and-ds}. As in the preceding theorem, the
following says (informally) that if~$F$ is a secure PRF, then this
domain-separated PRF construction is correct against adaptive
adversaries.
% \tsnote{Not really appropriate to say this next thing; I'll add a new section that addresses bigram DS-PRF hash.}
% We note that Neidermayer et
% al. in~\cite{xxx} suggest replacing the linear-PRF hash functions in
% the previous construction with independently keyed PRFs as a way to
% thwart their attacks.  The construction we consider now achieves the
% same end, albeit via explict domain separation rather than separate
% keys.

@@

\begin{theorem}[{\rm SS-privacy of bigram linear-PRF}]\label{thm:bi-lin-ss}
Let $\setprim_{\bilin}= (\Rep, \Qry)$ be the set-membership data
structure described in Figure~\ref{fig:neidermayer}, but with
$F_{K}$ replaced by a random function~$\rho$. Let
$\leak_{\mathsf{abl}}$ be the leakage function just described.
Let~$\elts=\{\mathrm{a,b,c}\}^*$. Let $n=3$,  $m=3\alpha $ for
integer $\alpha >> 1$, and let, $k = \lceil \ln(2) \alpha
\rceil$.\tsnote{This value of~$k$ is from the classical analysis for
minimizing the FP rate for a Bloom filter, and is set this way for
compatibility with classical results.  It isn't used in any
essential way in the proof sketch.}  Let~$A$ be the adversary in
Figure~\ref{fig:adv-bi-lin-ss}.  Then for any simulator $\Sim$, the
advantage
$\AdvPrivSS{\setprim_{\bilin},\leak_{\mathsf{abl}}}{A,\Sim}$ can be
made arbitrarily close to $1/2$ by choice of~$\alpha$.
\end{theorem}
\begin{proof}\tsnote{still a bit sketchy but believable}
On input the set~$S$ produced by~$A$, the $\Rep$ algorithm turns $x_1=$'cab', $x_2=$'bab' and $x_3$ into their respective bigram sets: $B_{x_1}=\{\sqcup\mathrm{c},\mathrm{ca},\mathrm{ab},\mathrm{b}\sqcup\}$, $B_{x_2}=\{\sqcup\mathrm{b},\mathrm{ba},\mathrm{ab}, \mathrm{b}\sqcup \}$; the set $B_{x_3}$ will be either $\{\sqcup\mathrm{c},\mathrm{ca},\mathrm{ab},\mathrm{ba}, \mathrm{a}\sqcup\}$, or $\{\sqcup\mathrm{c},\mathrm{ca},\mathrm{ab},\mathrm{bc}, \mathrm{c}\sqcup\}$, each with probability 1/2.  It then produces $\alpha$-bit arrays $M_1, M_2, M_3$ by hashing the corresponding bigram sets using the hash functions $h_j(s)=\rho_1(s)+ j\rho_2(s) \bmod m$.  Note that for sufficiently large~$m$, each of $M_1,M_2$ will contain exactly $4k$ positions set to 1; this is with overwhelming probability, up to collisions in the hash functions for different bigrams within a given bigram set.  Likewise, $M_{1,2}=M_1 \vee M_2$ will have exactly $6k$ positions set to 1, because $B_{x_1}$ and $B_{x_2}$ share $\mathrm{ab}$ and $\mathrm{a}\sqcup$.

@@

\begin{theorem}[{\rm Correctness of private-$M$ GBF in the ROM}]\fixme{FINISH! (Animesh?)}\label{thm:gbf-correctness}
Fix $k,m,n,r,\lambda>0$, and let $\setprim_{\mathrm{gbf}}=(\Rep, \Qry)$ be the private-$M$ garbled Bloom filter. For any adversary~$A$ that makes a total of~$q_T$ queries to the $\Test$ oracle, and $q_R$ queries to the RO, and has time-complexity~$O(t)$,
\[
\AdvCorrect{\setprim_{\mathrm{gbf}},r}{A} \leq  {\dbinom{q_T}{r}} \left( \dfrac{1}{2^{\lambda}} \right)^r\,.
\]
\end{theorem}
